The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-24 paper/paper.tex
paper: paren fixes
paper: increase size of tables
paper: explain cohl rewriting in all details (appendix?)
paper: more details in cohl
paper: corrections to verbose details of cohl
paper: use equality transports
paper: tweak breaks
paper: minor explanation

% For typesetting type theory rules
\newcommand \seqr[3]
  {\shortstack{$#2$ \\ \mbox{}\\
                   \mbox{}\hrulefill\mbox{}\\ \mbox{}\\ $#3$} \raisebox{2ex}{$\;\;\mbox{$#1$}$}}

@@

% The eqntable environment
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\NewEnviron{eqntable}[1]{
  \fontsize{7.2}{9}\selectfont
  \begin{tabularx}{0.94\linewidth}{
    @{}
    >{$}l<{$}
    >{$}c<{$}
    >{$}c<{$}
    >{$}Y<{$}
    @{}}
    \toprule
    \BODY
    \bottomrule
  \end{tabularx}
  \captionof{table}{#1}
}

@@

\begin{equation*}
  \begin{array}{llcl}
    \restrptype[n][\lbrack 0,p-1 \rbrack] &
    \fulldeps[n]                          & :      & \U                                                         \\
    \restrptype[n]                        & E      & \defeq                                         & \unittype \\
    \restrptype[n][\lbrack 0,p \rbrack]   &
    (\fulldeps[n])
                                          & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times             \\
                                          &        &                                                & \left(
    \begin{array}{l}
        \Pi q \leq n-p.\Pi \epsilon.\Pi d:\framep[n+1][p](\deps[n][\lbrack 0,p-1 \rbrack]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                                       \\ \painting[n][p](\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                                     \\
  \end{array}
\end{equation*}

@@

    (\depscohs[n][\lbrack 0,p \rbrack])     & \defeq                              &

@@

             (\overline{\deps}\left(\begin{array}{l}

@@

                               \end{array}\right))          . \\

@@

    \lambda d.\lambda l.\lambda \omega\overrightarrow{\cohf[n][p][q][0][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l_\omega)} \\

@@

\begin{equation*}
  \begin{array}{llcl}
    \restrp[n+1][p][q][\epsilon]        &
    \fulldepscohs[n]                    & :      &
    \left(
    \begin{array}{l}
        \Pi d:\framep[n+2][p]
        (\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
        \painting[n+2][p]
        (\overline{\fulldeps}(\fulldepscohs[n]))(d) \rightarrow  \\
        \painting[n+1][p](\fulldeps[n])
        (\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))\end{array}\right)                                        \\
    \restrp[n+1][n+1][q][\epsilon]      &
    (\fulldepscohs[n])                  & \defeq & \lambda d. \lambda (l,c). l\epsilon \\
    \restrp[n+1][p \leq n][q][\epsilon] &
    (\fulldepscohs[n])                  & \defeq & \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p \rbrack])(d)(l), \\
              \restrp[n+1][p+1][q][\epsilon](\fulldepscohs[n])(d,l)(c)             \\
            \end{array}\right)         \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \restrp[n+1][\lbrack 0,p-1 \rbrack] &
    \fulldepscohs[n]                    & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n])) \\
    \restrp[n+1]                        &
    \fulldepscohs[n]                    & \defeq & \unittype                                              \\
    \restrp[n+1][\lbrack 0,p \rbrack]   &
    \fulldepscohs[n]
                                        & \defeq &
    (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))             \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohptype[n][\lbrack 0,p-1 \rbrack] & \fulldepscohs[n] & :      & \U                                                           \\
    \cohptype[n]                        & \unitpoint       & \defeq & \unittype                                                    \\
    \cohptype[n][\lbrack 0,p \rbrack]   & \fulldepscohs[n] & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                        &                  &        & \left\{
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                                      \\
      \Pi d:\framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
      \restrp[n][p][q][\epsilon](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][r][\omega]
      (\fulldepscohs[n])(d)(c)) =                                                                                                                    \\
      \restrp[n][p][r][\omega](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][q+1][\epsilon]
      (\fulldepscohs[n])(d)(c))
    \end{array}
    \right.                                                                                                                        \\
  \end{array}
\end{equation*}

\subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws}

@@

    \cohl[n][p]                                 &
    \depscoht[n][\lbrack 0,p-1 \rbrack]         & :                                   &
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                          \\
      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} = \\
      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
    \end{array}                                                                              \\
    \cohl[n][p][q][r][\epsilon][\omega]         &
    \depscoht[n][\lbrack 0,p-1 \rbrack]         & \defeq                              &
    \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}{(\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                           \\
  \end{array}
\end{equation*}
where $\cohttype$ is:
\begin{equation*}
  \cohttype[n][p](\depscoht[n][\lbrack 0,p \rbrack]) \defeq
  \begin{array}{l}
    \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.                                                          \\
    \cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) \circ \\
    \ap\restrf[n][p][r][\omega](\cohf[n+1][p][q+1][0][\epsilon][\theta]
    (\depscoht[n][p]))
    \circ                                                                                                                            \\
    \cohf[n][p][q][r][\epsilon][\omega](\restrf[n+2][p][0][\theta](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) =       \\
    \ap\restrf[n][p][0][\theta](\cohf[n+1][p][q+1][r+1][\epsilon][\omega]
    (\depscoht[n][p]))
    \circ                                                                                                                            \\
    \cohf[n][p][q][0][\epsilon][\theta](\restrf[n+2][p][r+1][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack])))
    \circ                                                                                                                            \\
    \ap\restrf[n][p][q][\epsilon](\cohf[n+1][p][r][0][\omega][\theta]
    (\depscoht[n][p]))
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohp[n+1][p]                                &
    \fulldepscoht[n]                             & :      &
    \cohptype[n+1][p](\overline{\fulldepscohs}(\fulldepscoht[n]))                               \\
    \cohp[n+1][n+1][q][r][\epsilon][\omega]      &
    \fulldepscoht[n]
                                                 & \defeq & \lambda d. \lambda (l,c). l\epsilon \\
    \cohp[n+1][p \leq n][q][r][\epsilon][\omega] &
    \fulldepscoht[n]
                                                 & \defeq & \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \cohl[n][p][q][r][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)(l), \\
              \cohp[n+1][p+1][q][r][\epsilon][\omega](\fulldepscoht[n])(d,l))(c)              \\
            \end{array}\right)       \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohp[n+1][\lbrack 0,p-1 \rbrack] &
    \fulldepscoht[n]                  & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n])) \\
    \cohp[n+1]                        &
    \fulldepscohs[n]                  & \defeq & \unittype                                                \\
    \cohp[n+1][\lbrack 0,p \rbrack]   &
    \fulldepscoht[n]
                                      & \defeq &
    (\cohp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht[n]),\cohp[n+1][p](\fulldepscoht[n]))                 \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{lcl}
    \framep[n][\lbrack 0,n \rbrack]                                                                      & :      & \frametype[n][\lbrack 0,n \rbrack]                                     \\
    \painting[n][\lbrack 0,n \rbrack]                                                                    & :      & \paintingtype[n][\lbrack 0,n \rbrack](\framep[n][\lbrack 0,n \rbrack]) \\
    \restrf[n][\lbrack 0,n \rbrack]                                                                      & :      & \restrftype[n][\lbrack 0,n \rbrack]
    \left(
    \begin{array}{l}
        \framep[n][\lbrack 0,n \rbrack]   \\
        \painting[n][\lbrack 0,n \rbrack] \\
      \end{array}\right)                                                                                                                                                      \\
    \deps[n][\lbrack 0,n \rbrack]                                                                        & \defeq &
    \left(
    \begin{array}{l}
        \framep[n][\lbrack 0,n \rbrack]   \\
        \painting[n][\lbrack 0,n \rbrack] \\
        \restrf[n][\lbrack 0,n \rbrack]   \\
      \end{array}\right)                                                                                                                                                      \\
    \fulldeps[n](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U)                      & \defeq &
    \left(
    \begin{array}{l}
        \deps[n][\lbrack 0,n \rbrack] \\
        E                             \\
      \end{array}\right)                                                                                                                                                          \\
    \restrp[n][\lbrack 0,n \rbrack](E)                                                                   & :      & \restrptype[n][\lbrack 0,n \rbrack]
    (\fulldeps[n](E))                                                                                                                                                                      \\
    \cohf[n][\lbrack 0,n \rbrack](E)                                                                     & :      & \cohftype[n][\lbrack 0,n \rbrack]
    \left(
    \begin{array}{l}
        \fulldeps[n](E)                    \\
        \restrp[n][\lbrack 0,n \rbrack](E) \\
      \end{array}\right)                                                                                                                                                     \\
    \depscohs[n][\lbrack 0,n \rbrack](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U) & \defeq &
    \left(
    \begin{array}{l}
        \fulldeps[n](E)                    \\
        \restrp[n][\lbrack 0,n \rbrack](E) \\
        \cohf[n][\lbrack 0,n \rbrack](E)   \\
      \end{array}\right)                                                                                                                                                     \\
    \fulldepscohs[n]
    \left(\begin{array}{l}
              E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U                           \\
              E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack](E)))\rightarrow \U \\
            \end{array}\right)       & \defeq &
    \left(
    \begin{array}{l}
        \depscohs[n][\lbrack 0,n \rbrack](E) \\
        E'                                   \\
      \end{array}\right)                                                                                                                                                   \\
    \cohp[n][\lbrack 0,n \rbrack](E)(E')                                                                 & :      & \cohptype[n][\lbrack 0,n \rbrack]
    (\fulldepscohs[n](E)(E'))                                                                                                                                                              \\
  \end{array}
\end{equation*}

>>>>

@@

% The eqntable environment
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\NewEnviron{eqntable}[1]{
  \small
  \begin{tabularx}{0.94\linewidth}{
    @{}
    >{$}l<{$}
    >{$}c<{$}
    >{$}c<{$}
    >{$}Y<{$}
    @{}}
    \toprule
    \BODY
    \bottomrule
  \end{tabularx}
  \captionof{table}{#1}
}

@@

\begin{equation*}
  \begin{array}{llcl}
    \restrptype[n][\lbrack 0,p-1 \rbrack] &
    \fulldeps[n]                          & :      & \U                                                         \\
    \restrptype[n]                        & E      & \defeq                                         & \unittype \\
    \restrptype[n][\lbrack 0,p \rbrack]   &
    \fulldeps[n]
                                          & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times             \\
                                          &        &                                                & \left(
    \begin{array}{l}
        \Pi q \leq n-p.\Pi \epsilon.\Pi d:\framep[n+1][p](\deps[n][\lbrack 0,p-1 \rbrack]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                                       \\ \painting[n][p](\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                                     \\
  \end{array}
\end{equation*}

@@

@@

             \left(\overline{\deps}\left(\begin{array}{l}

@@

                                      \end{array}\right)\right)          . \\

@@

    \begin{array}{l}
      \lambda d.\lambda l.\lambda \omega.\overrightarrow{\cohf[n][p][q][0][\epsilon][\omega](d)}               \\
      \restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l_\omega) \\

@@

\begin{equation*}
  \begin{array}{llcl}
    \restrp[n+1][p][q][\epsilon]        &
    \fulldepscohs[n]                    & :      &
    \left(
    \begin{array}{l}
        \Pi d:\framep[n+2][p]
        (\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
        \painting[n+2][p]
        (\overline{\fulldeps}(\fulldepscohs[n]))(d) \rightarrow  \\
        \painting[n+1][p](\fulldeps[n])
        (\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))\end{array}\right)                                         \\
    \restrp[n+1][n+1][q][\epsilon]      &
    \fulldepscohs[n]                    & \defeq & \lambda d. \lambda (l,c). l_\epsilon \\
    \restrp[n+1][p \leq n][q][\epsilon] &
    \fulldepscohs[n]                    & \defeq & \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p \rbrack])(d)(l), \\
              \restrp[n+1][p+1][q][\epsilon](\fulldepscohs[n])(d,l)(c)             \\
            \end{array}\right)          \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \restrp[n+1][\lbrack 0,p-1 \rbrack] &
    \fulldepscohs[n]                    & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
    \restrp[n+1]                        &
    \fulldepscohs[n]                    & \defeq & \unittype                                             \\
    \restrp[n+1][\lbrack 0,p \rbrack]   &
    \fulldepscohs[n]
                                        & \defeq &
    (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))            \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohptype[n][\lbrack 0,p-1 \rbrack] & \fulldepscohs[n] & :      & \U                                                           \\
    \cohptype[n]                        & \unitpoint       & \defeq & \unittype                                                    \\
    \cohptype[n][\lbrack 0,p \rbrack]   & \fulldepscohs[n] & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                        &                  &        & \left\{
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                                       \\
      \Pi d:\framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])). \\
      \restrp[n][p][q][\epsilon](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][r][\omega]
      (\fulldepscohs[n])(d)(c)) =_{\cohf[n][p][q][r][\epsilon][\omega]}                                                                               \\
      \restrp[n][p][r][\omega](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][q+1][\epsilon]
      (\fulldepscohs[n])(d)(c))
    \end{array}
    \right.                                                                                                                        \\
  \end{array}
\end{equation*}
where we use the ``equality over'' notation $t =_e u$ to mean $\overrightarrow{e}(t) = u$ whenever $t$ is of some type $P(a)$, $u$ of type $P(b)$ and $e$ a proof of $a = b$.
\subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws}

@@

    \cohl[n][p]                                 &
    \depscoht[n][\lbrack 0,p-1 \rbrack]         & :                                   &
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                            \\
      \Pi d.\Pi l. {(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} =_{\cohf[n][p][r+1][q+1][\epsilon][\omega]} \\
      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
    \end{array}                                                                                            \\
    \cohl[n][p][q][r][\epsilon][\omega]         &
    \depscoht[n][\lbrack 0,p-1 \rbrack]         & \defeq                              &
    \begin{array}{l}
      \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}                                                                                         \\
      (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta]} (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])} (\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\
where $\cohttype$ is:
  \cohttype[n][p](\depscoht[n][\lbrack 0,p \rbrack]) \defeq
  \left(
  \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.                                                          \\
      \cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) \circ \\
      \ap\restrf[n][p][r][\omega](\cohf[n+1][p][q+1][0][\epsilon][\theta]
      (\depscoht[n][p]))
      \circ                                                                                                                            \\
      \cohf[n][p][q][r][\epsilon][\omega](\restrf[n+2][p][0][\theta](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) =       \\
      \ap\restrf[n][p][0][\theta](\cohf[n+1][p][q+1][r+1][\epsilon][\omega]
      (\depscoht[n][p]))
      \circ                                                                                                                            \\
      \cohf[n][p][q][0][\epsilon][\theta](\restrf[n+2][p][r+1][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack])))
      \circ                                                                                                                            \\
      \ap\restrf[n][p][q][\epsilon](\cohf[n+1][p][r][0][\omega][\theta]
      (\depscoht[n][p]))
  \right)
and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument of $\restrp$ and the deps argument)
  \Pi \theta.\left(
  \begin{array}{lcl}
    \begin{array}{l}
      \overrightarrow{\cohf[n][p][q][0][\epsilon][\theta]}
      \overrightarrow{\cohf[n+1][p][r][0][\omega][\theta]} \\
      (\restrp[n][p][q][\epsilon](\restrp[n+1][p][r][\omega](l_\theta)))
    \end{array} & =_{\cohf[n+1][p][q+1][r+1][\epsilon][\omega]} &
    \begin{array}{l}
      \overrightarrow{\cohf[n][p][r][0][\omega][\theta]}\overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta]} \\
      (\restrp[n][p][r][\omega](\restrp[n+1][p][q+1][\epsilon](l_\theta)))
  \right)
to
  \Pi \theta.\left(
  \begin{array}{lcl}
    \begin{array}{l}
      \overrightarrow{\cohf[n][p][q][0][\epsilon][\theta]}(\restrp[n][p][q][\epsilon] \\
      (\overrightarrow{\cohf[n+1][p][r][0][\omega][\theta]}\restrp[n+1][p][r][\omega](l_\theta)))
    \end{array} & =_{\cohf[n+1][p][q+1][r+1][\epsilon][\omega]} &
    \begin{array}{l}
      \overrightarrow{\cohf[n][p][r][0][\omega][\theta]}(\restrp[n][p][r][\omega] \\
      (\overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta]}\restrp[n+1][p][q+1][\epsilon](l_\theta)))
  \right)
which is exactly the type of $\cohl[n][p][q][r][\epsilon][\omega]$, up to functional extensionality relative to $\theta$.

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohp[n+1][p]                                &
    \fulldepscoht[n]                             & :      &
    \cohptype[n+1][p](\overline{\fulldepscohs}(\fulldepscoht[n]))                                \\
    \cohp[n+1][n+1][q][r][\epsilon][\omega]      &
    \fulldepscoht[n]
                                                 & \defeq & \lambda d. \lambda (l,c). l_\epsilon \\
    \cohp[n+1][p \leq n][q][r][\epsilon][\omega] &
    \fulldepscoht[n]
                                                 & \defeq & \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \cohl[n][p][q][r][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)(l), \\
              \cohp[n+1][p+1][q][r][\epsilon][\omega](\fulldepscoht[n])(d,l))(c)              \\
            \end{array}\right)        \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohp[n+1][\lbrack 0,p-1 \rbrack] &
    \fulldepscoht[n]                  & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\
    \cohp[n+1]                        &
    \fulldepscohs[n]                  & \defeq & \unittype                                               \\
    \cohp[n+1][\lbrack 0,p \rbrack]   &
    \fulldepscoht[n]
                                      & \defeq &
    (\cohp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht[n]),\cohp[n+1][p](\fulldepscoht[n]))                \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{lcl}
    \framep[n][\lbrack 0,n \rbrack]      & :      & \frametype[n][\lbrack 0,n \rbrack]                                     \\
    \painting[n][\lbrack 0,n \rbrack]    & :      & \paintingtype[n][\lbrack 0,n \rbrack](\framep[n][\lbrack 0,n \rbrack]) \\
    \restrf[n][\lbrack 0,n \rbrack]      & :      & \restrftype[n][\lbrack 0,n \rbrack]
    \left(
    \begin{array}{l}
        \framep[n][\lbrack 0,n \rbrack]   \\
        \painting[n][\lbrack 0,n \rbrack] \\
      \end{array}\right)                                                                                      \\
    \deps[n][\lbrack 0,n \rbrack]        & \defeq &
    \left(
    \begin{array}{l}
        \framep[n][\lbrack 0,n \rbrack]   \\
        \painting[n][\lbrack 0,n \rbrack] \\
        \restrf[n][\lbrack 0,n \rbrack]   \\
      \end{array}\right)                                                                                      \\
    \fulldeps[n](E)                      & \defeq &
    \left(
    \begin{array}{l}
        \deps[n][\lbrack 0,n \rbrack] \\
        E                             \\
      \end{array}\right)                                                                                          \\
    \restrp[n][\lbrack 0,n \rbrack](E)   & :      & \restrptype[n][\lbrack 0,n \rbrack]
    (\fulldeps[n](E))                                                                                                      \\
    \cohf[n][\lbrack 0,n \rbrack](E)     & :      & \cohftype[n][\lbrack 0,n \rbrack]
    \left(
    \begin{array}{l}
        \fulldeps[n](E)                    \\
        \restrp[n][\lbrack 0,n \rbrack](E) \\
      \end{array}\right)                                                                                     \\
    \depscohs[n][\lbrack 0,n \rbrack](E) & \defeq &
    \left(
    \begin{array}{l}
        \fulldeps[n](E)                    \\
        \restrp[n][\lbrack 0,n \rbrack](E) \\
        \cohf[n][\lbrack 0,n \rbrack](E)   \\
      \end{array}\right)                                                                                     \\
    \fulldepscohs[n](E)(E')              & \defeq &
    \left(
    \begin{array}{l}
        \depscohs[n][\lbrack 0,n \rbrack](E) \\
        E'                                   \\
      \end{array}\right)                                                                                   \\
    \cohp[n][\lbrack 0,n \rbrack](E)(E') & :      & \cohptype[n][\lbrack 0,n \rbrack]
    (\fulldepscohs[n](E)(E'))                                                                                              \\
  \end{array}
\end{equation*}
where
\begin{align*}
  E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U \\
  E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack](E)))\rightarrow \U
\end{align*}
